Barneby Lives usage example

### 2023-05-18 scripts/project_template.Rmd
reworked dates with lubridate

@@

  x_dmy <- x |> 
    mutate(across(.cols = c(!!coll_date_q, !!det_date_q), mdy2dmy,
           .names = "{col}_dmy"), .before = ncol(.)) |>
    mutate(across(.cols = c(!!coll_date_q, !!det_date_q), ~ lubridate::month(x),
           .names = "{col}_mo"))

  # add in collection dates here
#    if(missing(det_date)) {
#      with_date <- dplyr::mutate(x_dmy, coll_date_text = date2text(x_dmy, 'coll_date_dmy'))
##    } else {
#     with_date <-  dplyr::mutate(x_dmy, 
#           coll_date_text = date2text(x_dmy, 'coll_date_dmy'),
#           det_date_text  = date2text(x_dmy, 'coll_date_dmy'))
#    }

@@

fourtet <- data.frame(col_date = c('12/23/2003','07/09/2023', '1/13/2016'),
                   #   det_date = c('12/25/2003','07/09/2023', '1/13/2016'),
                      tet = c('abc', 'def', 'ggg'))

date_parser(fourtet, coll_date = 'col_date')

>>>>

  names_v <- c('_dmy', '_day', '_mo',  '_yr', '_text')
  column_names <- c(paste0(coll_date, names_v), paste0(det_date, names_v) )

@@

   x_dmy <- x |> 
    mutate(across(.cols = c(!!coll_date_q, !!det_date_q), lubridate::mdy, .names = "{.col}_dmy")) |>
    mutate(across(ends_with('_dmy'), ~ lubridate::month(.), .names = "{.col}_mo"),
           across(ends_with('_dmy'), ~ lubridate::day(.), .names = "{.col}_day"),
           across(ends_with('_dmy'), ~ lubridate::year(.), .names = "{.col}_yr")) |>
    mutate(across(.cols = c(!!coll_date_q, !!det_date_q), date2text, .names = '{.col}_text')) |>
    rename_with( ~ stringr::str_remove(., '_dmy'), matches("_dmy_.*$")) |>
    relocate(any_of(column_names), .before = last_col())

@@

fourtet <- data.frame(col_date = c('12/23/2003','07/09/2023', '1/13/2016'),
                      det_date = c('12/25/2003','07/09/2023', '1/13/2016'),
                      tet = c('abc', 'def', 'ggg'))

date_parser(fourtet, coll_date = 'col_date', det_date = 'det_date')
